---
title: "HuggingFace API Service"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HuggingFace API Service}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Creating a HuggingFace Account

- Visit [HuggingFace's website](https://huggingface.co/) and sign up for an account.
- Complete the account verification process.

### Creating a HuggingFace API Key

- After logging in, go to your account settings.
- Find the section for API keys and create a new one. Detailed guidance is available in HuggingFace's API documentation.

### Setting the HuggingFace API Key in .Renviron

To modify the `.Renviron` file:

```{r}
#| eval: false
require(usethis)
edit_r_environ()
```

For a persistent setting, add the following line to `.Renviron`, replacing `"<APIKEY>"` with your actual HuggingFace API key:

```bash
HF_API_KEY="<APIKEY>"
```

Save the file and restart your R session for the changes to take effect.

**Caution:** Remember to include `.Renviron` in your `.gitignore` file to prevent exposing your API key, especially if using version control systems like GitHub or GitLab.
