---
title: "OpenAI API Service"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OpenAI API Services}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Creating an OpenAI Account

- Visit [OpenAI's website](https://openai.com/) and sign up for an account.
- Follow the instructions to verify your account.

## Creating an OpenAI API Key

- Once logged in, navigate to the API section in your account settings.
- Follow the instructions to create a new API key. More detailed steps can be found in OpenAI's [API documentation](https://platform.openai.com/docs/).

## Setting the OpenAI API Key in .Renviron

To modify the `.Renviron` file:

```{r}
#| eval: false
require(usethis)
edit_r_environ()
```

For a persistent setting, add the following line to `.Renviron`, replacing `"<APIKEY>"` with your actual API key:

```bash
OPENAI_API_KEY="<APIKEY>"
```

Save the file and restart your R session for the changes to take effect.

**Caution:** Ensure `.Renviron` is included in your `.gitignore` file to avoid exposing your API key with version control systems like GitHub or GitLab.

**Important Note:** OpenAI API requires valid payment details in your OpenAI account to function. This is a restriction imposed by OpenAI and is unrelated to this package.
