---
title: "Perplexity"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Perplexity}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Creating an Perplexity Account

- Go to the [Perplexity website](https://perplexity.ai/) and sign up.
- Verify your account as instructed.

### Creating an Perplexity API Key

- Log into your Perplexity account and navigate to the [API documentation](https://docs.perplexity.ai/).
- Create an API key following their guidelines. Check Perplexity's API documentation for more details.

### Setting the Perplexity API Key in .Renviron

To modify the `.Renviron` file:

```{r}
#| eval: false
require(usethis)
edit_r_environ()
```

For a persistent setting, add the following line to `.Renviron`, replacing `"<APIKEY>"` with your actual Perplexity API key:

```bash
PERPLEXITY_API_KEY="<APIKEY>"
```

Save the file and restart your R session for the changes to take effect.

**Caution:** Ensure `.Renviron` is not exposed if using version control systems.
